### 2014-06-04 writing/S'14 paper/intro.tex

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in a wide array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,socher2013acl1},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging
about the ability of these models to learn compositional semantic
grammars, but it remains an open question whether they can achieve the
same results as grammars based in logical forms
\cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013} when it comes to core semantic
concepts like quantification, entailment and contradiction. To date,
experimental investigations of these concepts using distributed
representations have been largely confined to short phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment,kalchbrenner2014convolutional}.
For robust natural language understanding, we must be able to model
these phenomena in full generality on complex linguistic structures.

>>>>

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in a wide array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,socher2013acl1},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging
about the ability of these models to learn compositional semantic
grammars, but it remains an open question whether they can achieve the
same results as grammars based in logical forms
\cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013} when it comes to core semantic
concepts like quantification, entailment, and contradiction. To date,
experimental investigations of these concepts using distributed
representations have been largely confined to short phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment,kalchbrenner2014convolutional}.
For robust natural language understanding, we must be able to model
these phenomena in their full generality on complex linguistic structures.
